% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Lucas Xu}

\basicInfo{
  \email{sijialucas@gmail.com} \textperiodcentered\ 
  \phone{416-832-2812} \textperiodcentered\ 
  \linkedin[lucas-x]{https://www.linkedin.com/in/lucas-x/} \textperiodcentered\ 
  \github[Lucas Xu]{https://github.com/desperatecat}
  }

\section{Summary}
\datedline{Permanent Resident of Canada, 5+ years software test experience, 4+ years using Selenium Webdriver Automation Framework, looking for Software Developer in Test position.}{}



\section{Skills}
\begin{itemize}[parsep=0.5ex]
  \item Frontend: HTML5, CSS3, Sass, \textbf{JavaScript(ES6)}, Typescript, Bootstrap4, \textbf{React}, \textbf{Redux}, Vue.js
  \item Backend: \textbf{Java}, Spring MVC, \textbf{Spring Boot}, Python, Node.js, Express.js, JPA, Hibernate, MyBatis, Redis, Shiro, \textbf{MySQL}, PostgreSQL, MongoDB, RESTful API, HTTP, JSON
  \item Practice: Docker, Kubernetes, Azure, AWS, GCP, Jenkins, \textbf{Git}, Maven, Linux, Jira, \textbf{Agile}
  \item Test: \textbf{Selenium}, Junit, TestNG, Jest, \textbf{Postman}, SoapUI, JMeter
\end{itemize}


\section{Experience}
\datedsubsection{\textbf{Software Developer in Test}}{07.2019 -- Present}
\role{Rubikloud Technologies (https://rubikloud.com/)}{Toronto, ON}
\begin{itemize}
  \item Responsible for telemetry and test infrastructure, maintain code base to continuously run harnesses load tests and use-case tests for different modules with fully asynchronous Java.
  \item Design and develop internal monitoring/testing tools for promotion/customer lifecycle related SaaS products, such as QA benchmarking dashboard, stream data processing system for price/margin forecast, etc.
  \item Implement company-wide GCP QA environments migration leveraging Docker/Kubernete Ctl, build and improve a data engine platform for testing and validation upon CI pipeline.
  \item Collaborate with Technical Product Manger, Machine Learning Engineers, Application Developers and other QAs to standardize and enforce QA process and test coverage.
\end{itemize}

\section{Experience}
\datedsubsection{\textbf{Quality Assurance Engineer, Automation}}{04.2018 -- 06.2019}
\role{Tarion Warranty Corporation (https://www.tarion.com/)}{Toronto, ON}
\begin{itemize}
  \item Participated in business requirements gathering, user workflow identification and story estimiation meetings within an Agile Scrum environment, created test strategies/plans/cases.
  \item Built and refactored UI/API Automation Frameworks based on Java and Selenium Webdriver, converted 70\% manual testing cases to automation scripts, maintained script of cross-browser compatibilities.
  \item Executed test scripts through managing jobs with Jenkins, performed web service/gateway testing by Postman tools and executed performance load testing by JMeter.
  \item Conducted End to end testing (UI to DB) including functional, integration, regression, sanity/smoke testing. 
  \item Supported production maintenance, conducted periodic bug bashes of 30 participants, resulting in the discovery of, on average, 20\% of total bugs found. Troubleshootted and logged defects in Jira, then verified fixes.
\end{itemize}

\datedsubsection{\textbf{Software Test Specialist}}{06.2016 -- 04.2018}
\role{Pala Interactive (https://www.palainteractive.com/)}{Toronto, ON}
\begin{itemize}
  \item Participated in sprint planning meeting, defect triage meetings, scrum meeting and walkthrough meetings and recommended business work flow improvements.
  \item Built automation framework using Python, organized test cases with doctest and unittest, developed and executed test cripts to automate GUI elements of the web and mobile applications.
  \item Tested applications on client site to ensure the delivery of UAT, logged and tracked defects in JIRA.
  \item Performed the configuration file operation via pyyaml module, generated QA report via HTMLTestRunner, release note concerns and project status with an emphasis on project risk, including defect exit criteria and sign off decisions.
  \item Assisted in pilot deployments of new technologies to acquire performance, reliability and resolved production support incident tickets at customer sites during UAT session and customer training presentation deliveries.  
\end{itemize}

\datedsubsection{\textbf{Software QA Tester}}{06.2014 -- 03.2016}
\role{Kouding Network Tech. Co ---- Subsidy of Tencent}{Shenzhen, China}
\begin{itemize}
  \item Participated in planning, estimation and reviewed processes utilizing Agile testing methodologies with Scrum team; developed test plans against BA requirements or user stories among sprints.
  \item Strategized and executed quality assurance projects assigned by Project manager and QA manager, created preliminary business analysis of functional requirements to identify information, procedures, decision flows and/or corrective actions, assisted vendor resources in understanding the problem and performed system testing of vendor-provided fixes.
  \item Developed and maintained traceability matrix in between release cases, test cases and defect logs to cover functional/non-functional business acceptance criteria.

\end{itemize}



\section{Projects}{Portfolio Website: \emph{https://lucasxu.co}}
\datedsubsection{\textbf{Dev Connector Social Network Web}}{}
\datedline{Developed a MERN(React, Redux, Node.js, Express.js, MongoDB) stack project which includes React frontend components, JWT authentication, and extensive backend Express API. User can sign up/in, create profile with experience and education info, also can post and comment.}{}
\datedsubsection{\textbf{Project Tasks Management Tool}}{}{}
\datedline{Built a tool with React, Redux, Spring Boot, JPA and MySQL. It allow user to create project tasks, view and delete tasks. Moreover, user can update these tasks to different stage, i.e., TODO, IN PROGRESS, DONE.}{}
\datedsubsection{\textbf{Myblog Personal Blog}}{}
\datedline{Designed a personal blog system with Bootstrap, Spring Boot, MyBatis and Druid, which is Self-adaptive/Single-page/RESTful/Easy-to-manage\&release.}{}
\datedsubsection{\textbf{Online Shopping Management Portal}}{}
\datedline{Cooperated with a frontend developer to create a portal based on Vue, Spring Boot, Hibernate and MySQL, and was enhanced with middleware like Redis, Nginx and Shiro. The backend system includes commodity, order, category, customer, customer service management and payment platform. The frontend pages include personal center, shopping cart, product details page, submit order page, etc.}{}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{Education}
\datedsubsection{\textbf{Technology University of Eindhoven (TU/e)}, Eindhoven, The Netherlands}{}
\textit{Short-term Study} in Computer Systems
\datedsubsection{\textbf{University of Electronic Science \& Technology of China (UESTC)}, Chengdu, China}{}
\textit{B.Eng} in Computer Engineering, 3.89/4

%\section{Miscellaneous}
%\begin{itemize}[parsep=0.5ex]
%  \item Languages: English - Fluent, Mandarin - Native speaker
%\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
