% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Lucas Xu}

\basicInfo{
  \email{sijialucas@gmail.com} \textperiodcentered\ 
  \phone{416-832-2812} \textperiodcentered\ 
  \linkedin[lucas-x]{https://www.linkedin.com/in/lucas-x/} \textperiodcentered\ 
  \github[Lucas Xu]{https://github.com/desperatecat}
  }

\section{Summary}
\datedline{Permanent Resident of Canada, 2+ years software industrial experience, 1 year web application development, looking for full-stack/frontend/backend developer position.}{}



\section{Skills}
\begin{itemize}[parsep=0.5ex]
  \item Frontend: HTML5, CSS3, Sass, \textbf{JavaScript(ES6)}, Typescript, Bootstrap4, \textbf{React}, \textbf{Redux}, Vue.js
  \item Backend: \textbf{Java}, Spring MVC, \textbf{Spring Boot}, Android, Kotlin, Python, Node.js, Express.js, JPA, Hibernate, MyBatis, Redis, Shiro, \textbf{MySQL}, PostgreSQL, MongoDB, RESTful API
  \item Practice: Docker, Kubernetes, Azure, AWS, GCP, Jenkins, \textbf{Git}, Maven, Linux, Jira, \textbf{Agile}
  \item Test: Junit, Selenium, Jest, \textbf{Postman}, SoapUI, JMeter
\end{itemize}



\section{Projects}{Portfolio Website: \emph{https://lucasxu.co}}
\datedsubsection{\textbf{Dev Connector Social Network Web}}{}
\datedline{Developed a MERN(React, Redux, Node.js, Express.js, MongoDB) stack project which includes React frontend components, JWT authentication, and extensive backend Express API. User can sign up/in, create profile with experience and education info, also can post and comment.}{}
\datedsubsection{\textbf{Project Tasks Management Tool}}{}{}
\datedline{Built a tool with React, Redux, Spring Boot, JPA and MySQL. It allow user to create project tasks, view and delete tasks. Moreover, user can update these tasks to different stage, i.e., TODO, IN PROGRESS, DONE.}{}
\datedsubsection{\textbf{Myblog Personal Blog}}{}
\datedline{Designed a personal blog system with Bootstrap, Spring Boot, MyBatis and Druid, which is Self-adaptive/Single-page/RESTful/Easy-to-manage\&release.}{}
\datedsubsection{\textbf{Online Shopping Management Portal}}{}
\datedline{Cooperated with a frontend developer to create a portal based on Vue, Spring Boot, Hibernate and MySQL, and was enhanced with middleware like Redis, Nginx and Shiro. The backend system includes commodity, order, category, customer, customer service management and payment platform. The frontend pages include personal center, shopping cart, product details page, submit order page, etc.}{}





% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{Education}
\datedsubsection{\textbf{Technology University of Eindhoven (TU/e)}, Eindhoven, The Netherlands}{}
\textit{Short-term Study} in Computer Systems
\datedsubsection{\textbf{University of Electronic Science \& Technology of China (UESTC)}, Chengdu, China}{}
\textit{B.Eng} in Computer Engineering, 3.89/4

%\section{Miscellaneous}
%\begin{itemize}[parsep=0.5ex]
%  \item Languages: English - Fluent, Mandarin - Native speaker
%\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
